Flagging gravitational wave sources from radio jet morphology

### 2015-03-25 Paper/paper.tex
Add chirps to paper

>>>>

\begin{figure*}
\begin{center}
  \begin{tabular}{ccc}
    \includegraphics*[width=2.2in]{jet_i40_psi20_beta0_90_full.pdf} &
    \includegraphics*[width=2.2in]{jet_i40_psi20_beta0_90_zoom1.pdf} &
    \includegraphics*[width=2.2in]{jet_i40_psi20_beta0_90_zoom2.pdf}
  \end{tabular}
\end{center}
\caption{Jet morphology without accounting for opening angle
    evolution}
\label{fig:jet_nopsi}
\end{figure*}

\begin{figure*}
\begin{center}
  \begin{tabular}{ccc}
    \includegraphics*[width=2.2in]{jet_i40_beta0_90_full.pdf} &
    \includegraphics*[width=2.2in]{jet_i40_beta0_90_zoom1.pdf} &
    \includegraphics*[width=2.2in]{jet_i40_beta0_90_zoom2.pdf}
  \end{tabular}
\end{center}
\caption{Jet morphology with opening angle evolution.}
\label{fig:jet_psi}
\end{figure*}
